### 2015-01-11 paper/Content/03conclusion.tex
conclusion

\IEEEPARstart{I}{n} course of this research paper we have analyzed the characteristics given by the \emph{Android} SDK and have identified 
principle components which are generally used for developing an \emph{Android} applications. Those components have been examined regarding their composition and characteristics. 
Applying MVP offers various benefits like a better testability [……], but the paper has shown that it is often hard to define the roles 
of the \emph{Android} components considering MVP and to embed those components into the whole MVP model. But finally we can offer an MVP approach 
for \emph{Android} and a corresponding prototype app demonstrating how principle \emph{Android} components can be structured for applying MVP.

>>>>

\IEEEPARstart{I}{n} course of this research paper we have analyzed the characteristics given by the \emph{Android} SDK and have identified 
principle components which are generally used for developing \emph{Android} applications. Those components have been examined regarding their composition and characteristics. 
Finally we can offer an MVP approach for \emph{Android} and a corresponding prototype app demonstrating how principle \emph{Android} components can be structured for applying MVP.
